\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for Manipulator Kinematic Obstacle Avoidance

### 2024-03-18 Articles/IROS/root.tex
removed redundant parts

% PREDSTAVITEV REDUNDANCE

@@

% PREDSTAVITEV PRISTOPOV PLANIRANJA POTI V ROBOTIKI
The task of finding the joint trajectories of a manipulator is called motion planning~\cite{IDEASLab2023}. It consists of finding a sequence of joint configurations for a robot so that the robot can move along this path from its initial configuration to the goal configuration without colliding with itself, static obstacles or other agents in the environment. In addition to collision avoidance, motion planning for manipulators can optionally take into account various constraints, such as position, velocity, acceleration or jerk constraints for the joint angle or end effector, precision of the end effector with respect to position and orientation, stability of the manipulator, avoidance of singularities, or any number of other criteria.

@@

Various researchers have adopted different approaches to kinematic avoidance, as detailed in~\cite{c30, c39}.

Colbaugh and Glass (1989)~\cite{c31, c32} tackled this problem in a two-step process. Initially, they calculated the robot's end-effector trajectory. Subsequently, they used optimization to enhance the robot's dynamic response during trajectory execution and for tasks like obstacle avoidance.

@@

Many of the recent works focus on use of a variation of artificial potential field to plan motion of the manipulator. Xia et al.~\cite{c49} uses a variation of APF for manipulator motion~\cite{c49}. Park et al.~\cite{park2020trajectory} used a numerical Jacobian in combination with APF for motion planning. Zhang et al.~\cite{zhang2021obstacle} proposes dynamic repulsive field based on direction and speed between point on robot and obstacle, it also suggests decision making force that moves the robot away from certain local minima. Chen et al. proposes\remove{ an application }using APF in joint space and a variable kinematic optimization step~\cite{c50}. Long~\cite{c44} suggests creating motion plan of the manipulator using APF, he extends it using RRT to calculate virtual attractive point for the robot to move towards in case of local minima. Zhu et al.~\cite{c48} proposes use of APF in combination with MPC, to plan in environment with dynamic obstacles.

>>>>

@@

The task of finding the joint trajectories of a manipulator is called motion planning~\cite{IDEASLab2023}. It consists of finding a sequence of joint configurations for a robot so that the robot can move along this path from its initial configuration to the goal configuration without colliding with itself, static obstacles or other agents in the environment.

%In addition to collision avoidance, motion planning for manipulators can optionally take into account various constraints, such as position, velocity, acceleration or jerk constraints for the joint angle or end effector, precision of the end effector with respect to position and orientation, stability of the manipulator, avoidance of singularities, or any number of other criteria.

@@

%Various researchers have adopted different approaches to kinematic avoidance, as detailed in~\cite{c30, c39}.
%
%Colbaugh and Glass (1989)~\cite{c31, c32} tackled this problem in a two-step process. Initially, they calculated the robot's end-effector trajectory. Subsequently, they used optimization to enhance the robot's dynamic response during trajectory execution and for tasks like obstacle avoidance.

@@

Many of the recent works focus on use of a variation of artificial potential field to plan motion of the manipulator. Xia et al.~\cite{c49} uses a variation of APF for manipulator motion~\cite{c49}. Park et al.~\cite{park2020trajectory} used a numerical Jacobian in combination with APF for motion planning. Zhang et al.~\cite{zhang2021obstacle} proposes dynamic repulsive field based on direction and speed between point on robot and obstacle, it also suggests decision making force that moves the robot away from certain local minima.

%Chen et al. proposes\remove{ an application }using APF in joint space and a variable kinematic optimization step~\cite{c50}. Long~\cite{c44} suggests creating motion plan of the manipulator using APF, he extends it using RRT to calculate virtual attractive point for the robot to move towards in case of local minima. Zhu et al.~\cite{c48} proposes use of APF in combination with MPC, to plan in environment with dynamic obstacles.
%
